The Array of Long-Baseline Antennas for Taking Radio Observations from the Sub-Antarctic

### 2020-04-02 albatros_paper.tex
HCC updated autonomous station schematic + caption

\begin{figure}
  \begin{center}
    \includegraphics[width=1.0\linewidth]{Figures/albatros_2elem_schematic/albatros_2elem_schematic.pdf}
    \caption{Schematic for the two-element \albatros\ pathfinder.
      Signals from two dual-polarzation LWA antennas are amplified by
      front-end active baluns (\textcolor{red}{\bf citation for FEE}),
      and 100-m coaxial cables connect the antennas to the back-end
      readout electronics, which are housed in a Faraday cage denoted
      by the dashed box.  Each of the four antenna outputs is passed
      to a second-stage electronics chain consisting of a bias tee,
      amplifier, and high- and low-pass filters.  The signals are
      digitized at 250~Msamp/s by a SNAP board, and the on-board FPGA
      is programmed with firmware to perform a full cross-correlation
      of all four inputs.  A Raspberry Pi controls the SNAP board and
      also saves the computed spectra to an SD card.  Power to the
      system is provided by a bank of 12~V batteries and several
      regulated voltage outputs.}
    \label{Fig:albatros2_schem}
  \end{center}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\linewidth]{Figures/albatros_single_schematic/albatros_single_schematic.pdf}
    \caption{Schematic for single autonomous station pathfinder.
      \textcolor{red}{\bf Finish updating this figure.  Tankiso, Nivek, HCC?}}
    \label{Fig:Signal Chain}
  \end{center}
\end{figure}

@@

>>>>

\begin{figure}
  \begin{center}
    \includegraphics[width=1.0\linewidth]{Figures/albatros_2elem_schematic/albatros_2elem_schematic.pdf}
    \caption{Schematic for the two-element \albatros\ pathfinder.
      Signals from two dual-polarzation LWA antennas are amplified by
      front-end active baluns (\textcolor{red}{\bf citation for FEE}),
      and 100-m coaxial cables connect the antennas to the back-end
      readout electronics, which are housed in a Faraday cage denoted
      by the dashed box.  Each of the four antenna outputs is passed
      to a second-stage electronics chain consisting of a bias tee,
      amplifier, and high- and low-pass filters.  The signals are
      digitized at 250~Msamp/s by a SNAP board, and the on-board FPGA
      is programmed with firmware to perform a full cross-correlation
      of all four inputs.  A Raspberry Pi controls the SNAP board and
      also saves the computed spectra to an SD card.  The clock signal
      is provided by a Valon frequency synthesizer.  Power to the
      system is provided by a bank of 12~V batteries and several
      regulated voltage outputs.}
    \label{Fig:albatros2_schem}
  \end{center}
\end{figure}

@@

\begin{figure}
  \begin{center}
    \includegraphics[width=\linewidth]{Figures/albatros_single_schematic/albatros_single_schematic.pdf}
    \caption{Schematic for the single autonomous station pathfinder.
      Data and RF connections are outlined in black, and power
      connections are outlined in red.  A dual-polarization LWA
      antenna, equipped with an active balun, is connected 50-m
      coaxial cables to the back-end readout electronics, which are
      housed in a Faraday cage denoted by the dashed box.  Each of the
      two antenna inputs is passed to a second-stage electronics chain
      consisting of a bias tee, high- and low-pass filters, and
      amplifier.  The signals are digitized at 250~Msamp/s by a SNAP
      board, and the on-board FPGA is programmed with firmware that
      computes averaged auto- and cross-spectra, as well as
      channelized baseband.  A Raspberry Pi controls the SNAP board
      and saves the data products to a combination of an SD card and
      external hard drives.  Timing information is provided by a
      GPS-discipined clock.  Power to the system is provided solar
      panels that charges a 24-V battery bank, which is regulated down
      to several other output levels.}
    \label{Fig:Signal Chain}
  \end{center}
\end{figure}

@@

\subsection{Readout electronics}
\textcolor{red}{\bf Nivek, Jon?} \\
Text here about one-bit stuff, pushing baseband through the RPi3,
clock requirements, data rates, etc.
